The analogy of the cohort-equations paradigm to the compartmental epidemic models

### 2021-06-07 cohort.tex
details added to the SIR withtesting example

\newcommand{\fref}[1]{Fig.~\ref{#1}}
\newcommand{\Rlogo}{R\xspace}
\newcommand{\percap}{\emph{per capita}\xspace}
\newcommand{\R}{\ensuremath{\mathcal{R}_0}}
\newcommand{\covid}{COVID-19\xspace}
\newcommand{\pro}[1][]{\ensuremath{\frac{\partial #1}{\partial \rho}}}
\newcommand\pder[2][]{\ensuremath{\frac{\partial#1}{\partial#2}}} %\pder[x]{y}
\renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}} %bold font for vector

@@

\begin{note}
The following notes/points are to be considered in moving from one framework to another, namely, cohort framework \citep{champredon2018equivalence} and comartmental framework \citep{van2002reproduction}; 
\begin{enumerate}
\item
In the compartment framework, steps 2 and 3 are combined.
\item
If the initial condition $\vec I(0)$ of the cohort Eq.~\eqref{eq:I} (in the cohort framework) is chosen as the principal eigenvector of the next-generation matrix $FV^{-1}$ corresponding to $\R$ (in compartmental framework), the next generation vector $\vec G$~\eqref{eq:ng} would be 
\begin{equation}
\vec G = FV^{-1} \vec I(0) = \R \vec I(0).
\end{equation}
Thus, in this case inorder to collapse $\vec G$ to $\R$, if $\vec I(0)$ is a unit vector as well, i.e., $\lVert \vec I(0) \rVert = 1$, it follows that $\vec I(0)^t \cdot \vec G = \R$, where $\vec I(0)^t$ is the transpose of $\vec I(0)$.
\end{enumerate}
\end{note}

@@

{\it Step 3;} The next-generation vector is 
\begin{align}
\vec G=\int_0^\infty \vec K(\tau) d\tau
=\beta\,\frac{\sigma}{\gamma-\sigma}\,\Big(\left[ \begin{array}{c} 1/\sigma-1/\gamma\\0 \end{array} \right]\Big)
=\left[ \begin{array}{c} \beta/\gamma\\0 \end{array} \right].
\end{align}

@@

{\it Step 1;} The cohort Eq.~ is
\begin{align}
\vec I'=-V\,\vec I,~~ \text{where}~~ \vec I(\tau)=\left[ \begin {array}{c} I\_u(\tau)\\I_n(\tau)\\I_p(\tau)\\I_c(\tau) \end {array} \right], ~~
\vec I(0)=\left[ \begin {array}{c} S\_u^*\\(1-\theta\_w)S\_n^*\\0\\0 \end {array} \right].
\end{align}
Solving for $\vec I(\tau)$ by finding the eigenvalues and eigenvectors of the above linear system results in
\begin{align}
\vec I(\tau)=&
c_1\,\exp(-\gamma\,\tau)\,\left[ \begin {array}{c} 0\\0\\0\\1 \end {array} \right] 
+c_2\,\exp(-(F_I+\gamma)\,\tau)\,\left[ \begin {array}{c} \frac{F_I-\omega}{\omega}\\0\\\frac{-F_I}{\omega}\\1 \end {array} \right]
+c_3\,\exp(-(\omega+\gamma)\,\tau)\,\left[ \begin {array}{c} 0\\0\\-1\\1 \end {array} \right] \\\notag
+& c_4\,\exp(-(\omega+\gamma)\,\tau)\,\Big(\tau\,\left[ \begin {array}{c} 0\\0\\-1\\1 \end {array} \right]+
\left[ \begin {array}{c} \frac{-1}{F_I}\\ \frac{\omega-F_I}{F_I\,\omega}\\ \frac{1}{\omega}\\0 \end {array} \right]\Big),
\end{align}
where 
\begin{align}
c_1=&1\\
c_2=&\frac{\omega}{F_I-\omega}(S\_u^*-\frac{\omega}{F_I-\omega}\,S\_n^*)\\
c_3=&\frac{-F_I}{F_I-\omega}(1-\frac{\omega}{F_I-\omega}S\_n^*)\\
c_4=&\frac{-\omega\,F_I}{F_I-\omega}S\_n^*.
\end{align}

@@

{\it Step 3;} The next-generation vector is $\vec G$ as follows.
\begin{align}
\vec G=&\int_0^\infty \vec K(\tau) d\tau\\
=&
\end{align}
%%%%%%%%%%%%%%%%%%%%
\section{Ideas-Unknowns}
- Collapsing the vectorized kernek $\vec K(\tau)$ into a scalar function of time.

>>>>

\newcommand{\fref}[1]{Fig.~\ref{#1}}
\newcommand{\Rlogo}{R\xspace}
\newcommand{\percap}{\emph{per capita}\xspace}
\newcommand{\R}{\ensuremath{\mathcal{R}_0}}
\newcommand{\covid}{COVID-19\xspace}
\newcommand{\pro}[1][]{\ensuremath{\frac{\partial #1}{\partial \rho}}}
\newcommand\pder[2][]{\ensuremath{\frac{\partial#1}{\partial#2}}} %\pder[x]{y}
\renewcommand{\vec}[1]{\ensuremath{\mathbf{#1}}} %bold font for vector
\newcommand{\e}{\ensuremath{{\rm e}}}

@@

\begin{note}
The following notes/points are to be considered in moving from one framework to another, namely, cohort framework \citep{champredon2018equivalence} and comartmental framework \citep{van2002reproduction}; 
\begin{enumerate}
\item
In the compartment framework, steps 2 and 3 are combined.
\item
If the initial condition $\vec I(0)$ of the cohort Eq.~\eqref{eq:I} (in the cohort framework) is chosen as the normalized principal eigenvector of the next-generation matrix $FV^{-1}$ corresponding to $\R$ (in compartmental framework), the next generation vector $\vec G$~\eqref{eq:ng} would be 
\begin{equation}
\vec G = FV^{-1} \vec I(0) = \R \vec I(0).
\end{equation}
Thus, in this case inorder to collapse $\vec G$ to $\R$, when $\vec I(0)$ is the normalized initial distribution of infected individuals, i.e., $\lVert \vec I(0) \rVert = 1$, it follows that $\vec I(0)^t \cdot \vec G = \R$, where the row vector $\vec I(0)^t$ is the transpose of $\vec I(0)$.
\end{enumerate}
\end{note}

@@

{\it Step 3;} The next-generation vector is 
\begin{align}
\vec G=\int_0^\infty \vec K(\tau) d\tau
=\beta\,\frac{\sigma}{\gamma-\sigma}\,\Big(\left[ \begin{array}{c} 1/\sigma-1/\gamma\\0 \end{array} \right]\Big)
=\left[ \begin{array}{c} \beta/\gamma\\0 \end{array} \right].
\end{align}
Note that, $\R =\vec I(0)^t \cdot \vec G =\beta/\gamma$.

@@

{\it Step 1;} The cohort Eq.~ is
\begin{align}
\vec I'=-V\,\vec I,~~ \text{where}~~ \vec I(\tau)=\left[ \begin {array}{c} I\_u(\tau)\\I_n(\tau)\\I_p(\tau)\\I_c(\tau) \end {array} \right], ~~
\vec I(0)=\left[ \begin {array}{c} \frac{S\_u^*}{(1-\theta\_w)S\_n^*}\\1\\0\\0 \end {array} \right].
\end{align}
Solving for $\vec I(\tau)$ by finding the eigenvalues and eigenvectors of the above linear system results in
\begin{align}
\vec I(\tau)=&
\left[ \begin {array}{cccc}  
\frac{F_I-\omega}{\omega} \e^{-(F_I+\gamma)\tau}&0&0&\frac{-1}{F_I}\e^{-(\omega+\gamma)\tau}\\
0&0&0&\frac{F_I-\omega}{-F_I\omega} \e^{-(\omega+\gamma)\tau}\\
\frac{-F_I}{\omega} \e^{-(F_I+\gamma)\tau}&0&-\e^{-(\omega+\gamma)\tau}&(\frac{1}{\omega}-\tau)\e^{-(\omega+\gamma)\tau}\\
\e^{-(F_I+\gamma)\tau}&\e^{-\gamma\tau}&\e^{-(\omega+\gamma)\tau}&\tau\e^{-(\omega+\gamma)\tau}
\end {array} \right] \vec c,
\end{align}
where 
\begin{align}
\vec c =
\left[ \begin {array}{c} -{\frac {\omega\, \left(  \left( -\omega\,
\theta_{{w}}+{\it F_I} \right) {\it S\_u}+\omega\,\theta_{{w}}-\omega
 \right) }{ \left( {\it F_I}-\omega \right) ^{2} \left( -1+\theta_{{w
}} \right) {  S\_n}}}\\ \noalign{\medskip}{\frac {-{ S\_u}\,
\theta_{{w}}-1+\theta_{{w}}}{ \left( -1+\theta_{{w}} \right) { S\_n
}}}\\ \noalign{\medskip}-{\frac {{ F_I}\, \left(  \left( -\omega-{
 F_I}\,\theta_{{w}}+2\,\omega\,\theta_{{w}} \right) { S\_u}-{
 F_I}+{ F_I}\,\theta_{{w}}+2\,\omega-2\,\omega\,\theta_{{w}}
 \right) }{ \left( { F_I}-\omega \right) ^{2} \left( -1+\theta_{{w
}} \right) { S\_n}}}\\ \noalign{\medskip}-{\frac {{ F_I}\,
\omega}{{ F_I}-\omega}}\end {array} \right] .
\end{align}

@@

{\it Step 3;} The next-generation vector is $\vec G$ as follows.
\begin{align}
\vec G=&\int_0^\infty \vec K(\tau) d\tau\\
=& \R\, \vec I(0), 
\end{align}
where $\R$ is calculated in the previous work.
%%%%%%%%%%%%%%%%%%%%
\section{Ideas-Unknowns}
- Collapsing the vectorized kernek $\vec K(\tau)$ into a scalar function of time.
